---
title: "Exploratory Data Analysis"
output: html_notebook
---

```{r}
library(tidyverse)
library(Hmisc)
```


```{r}
appstore_df <- read.csv("../Data/AppleStore.csv")
appstore_df %>% arrange(X)
describe(appstore_df)
```

```{r}
appstore_df <- mutate(appstore_df, size_mb = size_bytes/1000000)
appstore_df <- mutate(appstore_df, is_free = price == 0)
appstore_df <- mutate(appstore_df, user_rating_string = as.character(user_rating))
head(appstore_df)
```
We will first add certain variables to the data set that are more relevant (like total size of an app in megabytes and if the app is free/paid).

```{r}
appstore_df %>% ggplot() + geom_boxplot(mapping = aes(x=prime_genre, y = rating_count_tot, color=prime_genre)) + scale_y_log10() + coord_flip() + labs(y="Rating Count (logarithmic)") + labs(x="App Primary Genre") + theme_minimal()
```

Since a total downlaod count is not available in this dataset due to restrictions from Apple, we will treat the total rating count of an app to be a rough estimate of its total downloads. A higher rating count implies that the app is more successful.
We can see how the popularity of every app genre with the graph above. The app genre plays a minor impact in the success of an app (exception is the Book genre).

```{r}
appstore_df %>% ggplot() + geom_bar(mapping=aes(x=is_free, fill=is_free)) + labs(x="App is Free") + theme_minimal()
```
We can see that there are more free apps in the Apple App Store than paid apps, which can range from \$0.99 to \$299.99.

```{r}
appstore_df %>% ggplot() + geom_col(mapping=aes(x=is_free, y=rating_count_tot, fill=is_free)) + labs(x="App is Free") + theme_minimal()
```
The total rating count, which implies the total download count, of free apps are much higher than paid apps. This ratio is significantly higher than the number of free apps to paid apps, which implies that free apps are typically more successful in the App Store.

```{r}
appstore_df %>% ggplot() + geom_histogram(mapping = aes(x=size_mb), bins = 60) + geom_vline(mapping= aes(xintercept= median(appstore_df$size_mb)), color="#873096") + geom_vline(mapping= aes(xintercept= mean(appstore_df$size_mb), color="#ff6159")) + theme_minimal()
``` 
We can see the distribution of the app sizes throughout the ~7000 apps in the data set. The red line represents the mean of the app sizes in megabytes, while the purple line represents the median of the app sizes in megabytes. We can see that most apps are under the 500 MB threshold.

```{r}
appstore_df %>% ggplot() + geom_point(mapping = aes(y=size_mb, x=log10(rating_count_tot), color=prime_genre == "Games", alpha=0.8)) + theme_minimal()
```
 

This scatterplot outlines many aspects about the data that we're investigating. The most striking aspect is that most of the apps in the dataset fall into the Games category, as  you can see with the blue coloring. Also, most of the apps with greater than 1 GB download size are in fact games. Every other app category mostly falls under the 1 GB download size. In addition, the super-popular apps to the far right of the graph typically do not exceed the 2 GB threshold.

```{r}
appstore_df %>% ggplot() + geom_boxplot(mapping = aes(x=cont_rating, y = rating_count_tot, color=cont_rating)) + scale_y_log10() + coord_flip() + labs(y="Rating Count (logarithmic)") + labs(x="Content Rating") + theme_minimal()
```

We could see that content rating plays a very minor roll in determining the success of an app. 

```{r}
appstore_df %>% ggplot() + geom_boxplot(mapping = aes(x=user_rating_string, y = rating_count_tot, color=user_rating_string)) + scale_y_log10() + coord_flip() + labs(y="Rating Count (logarithmic)") + labs(x="User Review Rating") + theme_minimal()
```
From the boxplot above, we can see a clear growth in total ratings (which gives a rough indication of total downloads) until the user ratings goes above 1.5 stars. However, from 2 - 5 stars, the difference in rating count cannot be determined from the graph.

## Summary
- Content rating does not affect an app's success.
- If the user rating is below 1.5, an app's success is harmed.
- Most incredibly popular apps have a total size below 2 gigabytes or 2000 megabytes.
- Most apps that are over 1 GB are usually games.
- Free apps have significantly more downloads than paid apps.